Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-28 sections/eval.tex
Update on Overleaf.
update

\help{The main points of this section are:}

\help{1. summarize the difference between inner, gustavson, and outer, cite gamma but this also needs to stand on it's own}

\help{2. Explain why bytemap temporary makes sense for gustavson, but not for outer or inner}

\help{3. Point out that TACO does not even support outer product because it does not support scatter into 2D workspace}

\help{4. Take a look at the figure and point out that Finch is competitive with TACO on inner and gustavson, and that for outer product we see what we would expect from TACO: i.e. Finch Outer with dense performs similarly to TACO with dense, and Finch Outer with sparse performs much better as the matrix size increases.}

\help{5. point out that for the large matrices finch is competitive with TACO for gustavson}.

\help{6. explain the features of "datastructure-driven programming" that are used here in this problem. i.e. explicit temporary, bytemap format, transpositions}.
\begin{figure}
    \label{fig:spgemm}
	\includegraphics[width=0.5\linewidth]{spgemm_small_speedup_log_scale.png}%
	\includegraphics[width=0.5\linewidth]{spgemm_joel_speedup.png}
    \caption{A comparison of several matrix multiplication algorithms between
    Finch and Taco. On left, we use smaller matrices, ordered from small to big
    dimension. Note that inner products necessarily requires $O(n^2)$ work and
    taco's outer products format is dense. Finch can use a sparse outer products
    format and thus has an asymptotic advantage that becomes evident as the
    output dimensions grow. On right, we use only gustavson's algorithm and compare on larger matrices.}
\end{figure}

@@

\subsubsection{Graph Analytics}
\help{In this case, the two main highlights are that Finch can do arbitrary operators (i.e. choose), and that Finch can do early break, and also the different loop orders and multiple outputs. We may need to explain a little bit about what push pull is. For bellman, the main point is that we need multiple outputs, sparse inputs, masks, and sparse outputs with differing formats at differing points.}

>>>>

%\help{The main points of this section are:}

%\help{1. summarize the difference between inner, gustavson, and outer, cite gamma but this also needs to stand on it's own}

%\help{2. Explain why bytemap temporary makes sense for gustavson, but not for outer or inner}

%\help{3. Point out that TACO does not even support outer product because it does not support scatter into 2D workspace}

%\help{4. Take a look at the figure and point out that Finch is competitive with TACO on inner and gustavson, and that for outer product we see what we would expect from TACO: i.e. Finch Outer with dense performs similarly to TACO with dense, and Finch Outer with sparse performs much better as the matrix size increases.}

%\help{5. point out that for the large matrices finch is competitive with TACO for gustavson}.

%\help{6. explain the features of "datastructure-driven programming" that are used here in this problem. i.e. explicit temporary, bytemap format, transpositions}.
\begin{figure}
    \label{fig:spgemm}
	\includegraphics[width=0.5\linewidth]{spgemm_small_speedup_log_scale.png}%
	\includegraphics[width=0.5\linewidth]{spgemm_joel_speedup.png}
    \caption{A comparison of several matrix multiplication algorithms between
    Finch and Taco. On left, we use smaller matrices, ordered from small to big
    dimension. Note that inner products necessarily requires $O(n^2)$ work and
    taco's outer products format is dense. Finch can use a sparse outer products
    format and thus has an asymptotic advantage that becomes evident as the
    output dimensions grow. On right, we use only gustavson's algorithm and compare on larger matrices.}
\end{figure}

@@

\subsubsection{Graph Analytics}
%\help{In this case, the two main highlights are that Finch can do arbitrary operators (i.e. choose), and that Finch can do early break, and also the different loop orders and multiple outputs. We may need to explain a little bit about what push pull is. For bellman, the main point is that we need multiple outputs, sparse inputs, masks, and sparse outputs with differing formats at differing points.}
